---
title: "Introducing the PrevCorr package"
author: "cheungngo"
date: "26 February 2021"
output: html_document
---

##### This package is developed to allow high-throughput statistical calculation for prevalence-correlate studies.  Many useful functions were included, and users can produce hundreds clumpsy confusion tables at a time, do hundreds of multivariate logistic regressions at a time, or hundreds of tests for multicollinearity at a time, etc.  With the use of this package, the time for statistical analysis would be much much reduced, and the results would be readily reproducible and repeatable.


### Preparing the environment

```{r, eval=FALSE}
### Installing the package

install.packages("devtools") # devtools required to install packages from github
library(devtools)

devtools::install_github("cheungngo/PrevCorr") # installing the "PrevCorr" package
```

```{r, message=FALSE}
### Loading the library

library(PrevCorr)
```


### Format of dataframe required

```{r, message=FALSE}
### Loading the data
# Data not included in the package

# separate files for dependent and independent variables
library(readr)
dependent_var <- read_csv("~/dependent_var.csv")
masterdata_A <- read_csv("~/masterdata_A.csv")
masterdata_B <- read_csv("~/masterdata_B.csv")
```

```{r}
### Format of the dataframe for dependent variables

# Need to follow the rules to let the functions work
# each row for one subject
# for binary outcome, 0 for no; 1 for yes (i.e. 0 for no condition, 1 for condition present)
# functions written in this package are mostly for binary outcome, please contact author for other possible variations

dependent_var[1:10,c(1, 14)] # a portion of dataframe
```

```{r}
### Format of the dataframe for independent variables

# Need to follow the rules to let the functions work
# each row for one subject

# for categorical variables (i.e. education, welfare, marital, etc), just use numbers to represent each category; if binary => 1 and 2
# for continuous variables (i.e. age, sex_no_per_mo, sex_partner_no, etc), can simply input the numbers
# inputing "0" represents no entry, but it might be regarded as an extra category for categorical variables; for continuous variables, we have functions to include or exclude those "0"s as sometimes "0" means zero but not no entry

masterdata_A[1:10,c(14, 16:17, 13, 18:19)] # a portion of dataframe
```


### Useful functions from this package

```{r, eval=FALSE}
### You can view the documentation of all functions in the package using the following codes

help(package = "PrevCorr")
```

```{r}
### Getting the column number

# First you need to get the column numbers for your concerned variables
# you can simply visualize using names(#concerned dataframe)

names(dependent_var) # this serves an example
```

```{r}
### Serial Shapiro-Wilk test

# Shapiro-Wilk test is performed to see if the variables were normally distributed, thus to guide subsequent tests (i.e. t-test or Wilcoxon)

ind = c(13, 55:57, 19, 18, 97, 98) # these numbers represents the column number of the concerned variable in the dataframe

serial_shapiro(masterdata_A, ind) # this gives all the results for the concerned variables; note that "masterdata_A" is the dataframe concerned
# serial_shapiro(data, cols)
# data : the dataframe concerned
# cols : the columns of the variable in the dataframe concerned

```

```{r}
### Frequency of occurence for multiple variables

# This is to calculate the frequency of occurences of many categorical variables at a time

indb = c(3:5,2) # these numbers represents the column number of the concerned variable in the dataframe; of course there could be more

serial_foo(masterdata_B, indb)
# serial_foo(data, cols)
# data : the dataframe concerned
# cols : the columns of the variable in the dataframe concerned
```

```{r}
### Median and IQR

# This is to calculate the median and IQR for continuous variables (that were not of normal distributions)

ind = c(13, 55:57, 19, 18, 97, 98) # these numbers represents the column number of the concerned variable in the dataframe

serial_miqr(masterdata_A, ind)
# serial_miqr(data, cols)
# data : the dataframe concerned
# cols : the columns of the variable in the dataframe concerned
```

```{r}
### A series of confusion tables

# This is to produce the confusion tables for categorical variables

ind = c(14:17) # these numbers represents the column number of the concerned variable in the dataframe

serial_tab(dependent_var, # the dataframe for dependent variables
           masterdata_A, # the dataframe for independent variables
           1, # 1 being the column number of the dependent variable concerned
           ind)
```

```{r}
### A series of fisher exact tests

# Many fisher exact tests at a time

ind = c(14:17) # these numbers represents the column number of the concerned variable in the dataframe

serial_fisher(dependent_var, # the dataframe for dependent variables
              masterdata_A, # the dataframe for independent variables
              1, # 1 being the column number of the dependent variable concerned
              ind)

### Note that we also have functions for chi-square tests! Similar way of use
### serial_chisq()
```

```{r}
### Serial MWW (wilcoxon) tests

# Many wilcoxon tests at a time

ind = c(13, 55:57, 19, 18, 97, 98) # these numbers represents the column number of the concerned variable in the dataframe

serial_wilcox(dependent_var, # the dataframe for dependent variables
              masterdata_A, # the dataframe for independent variables
              1, # 1 being the column number of the dependent variable concerned
              ind)

### Explaining the output table
# column 1: dependent var
# column 2: independent var
# column 3: wilcoxon stat
# column 4: p-value
# column 5 and 6: median and iqr for the respective group (grouped by dependent var = 0 and 1)

### Note that for variables with normal distribution we can use serial_t() in the same package
```

```{r}
### Serial logistic regressions (with adjustments) for categorical variables at a time

adj = c(13, 42:46, 53, 61) # these numbers represents the column numbers of the concerned variable for adjustment in the dataframe; these would be repeated for each analysis for the concerned variables
ind = c(14, 16:17) # these numbers represents the column numbers of the concerned variable for analysis in the dataframe

serial_logregka(dependent_var, # the dataframe for dependent variables
                masterdata_A, # the dataframe for independent variables
                1, # 1 being the column number of the dependent variable concerned
                ind, 
                1, # The category for reference
                adj)

# another example with a different category for reference
serial_logregka(dependent_var, 
                masterdata_A, 
                1, 
                15, # different variable
                2, # different category for reference
                adj)

### Explaining the output table
# column 1: variable name
# column 2: Odds ratio and CI
# column 3: p-value

### Note that there are functions for logistic regressions with continuous variables as well, e.g.:
# serial_logregkacont(); which excludes "0" values from analysis
# serial_logregkacont0(); which includes "0" values from analysis 
```

```{r, warning=FALSE}
### VIFs for a series of multivariate logistic regressions (categorical variables)

adj = c(13, 42:46, 53, 61) # these numbers represents the column numbers of the concerned variable for adjustment in the dataframe; these would be repeated for each analysis for the concerned variables
ind = c(23:24, 47:49, 62:63) # these numbers represents the column numbers of the concerned variable for analysis in the dataframe

serial_vif(dependent_var, # the dataframe for dependent variables
           masterdata_A, # the dataframe for independent variables
           1, # 1 being the column number of the dependent variable concerned
           ind, 
           1, # The category for reference
           adj)

### Note that there are functions for VIFs for logistic regressions with continuous variables as well, e.g.:
# serial_vif_cont(); which excludes "0" values from analysis
# serial_vif_cont_0(); which includes "0" values from analysis
```


### Output of results

```{r, warning=FALSE}
### The output of results is simple
### For each analysis, pass the calculation to an object, i.e.

result = serial_logregka(dependent_var, masterdata_A, 1, ind, 1, adj)

### And then export the object with the following code:

write.csv(result, # the concerned object
          "~/testingresults.csv", # output filename
          row.names = T)

### the output file could be read by excel, and should be readily presentable as the final table in the dissertation with some standard formatting
```


##### The above demonstration does not include all the functions in the package.  Other interesting functions include those for classifying anti-depressants into respective classes, calculating equivalent SSRI dosage, data wrangling, and functions to facilitate step-wise multivariate regressions.  Please contact author for further queries.
